\documentclass[a4paper]{article}

%\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage[legalpaper, portrait, margin=2in]{geometry}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{float}
\usepackage{pythontex} 
\usepackage{biblatex} %Imports biblatex package
\addbibresource{ref.bib} %Import the bibliography file

\title{EDP01 Artificial Intellegence: Assignment 1}
\author{Alfred Langerbeck, al5878la-s}

\begin{document}

\maketitle

\section{Intro}
The following report will present the second assignment for the Artificial intelligence course. The assignemnt conssisted of a jupyter notebook where machine learning was used to approximate the word count in a text from the number of "A" characters i said text. First linear regression was used to create the model for prediction. The weights was calculated using the gradient descent method where both batch and stochastic descent was implemented. Secondly the previous model was used to create a classification model used to determine if a text is either french or english. The classification was then repeated using logistical regression. Both models created was visualized and then evaluated using "leave one out cross validation". Finnally two popular ML APIs: sklearn and Keras was used to achive the same result. The data set used for training and evaluation where the fifteen chapter of the book Salammbô (1862) by Gustave Flaubert both in original french and english.

The assignment also included 
 
\section{The assignment}

\subsection{Implementation}

\subsection{Results}

\section{Paperstudy: An overview of gradient descent optimization algorithms}


\end{document}